\documentclass[letterpaper,11pt]{article}
\usepackage{resume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{\Large Longqi (Rocky) Cai} & 412-652-8030 \\
\multirow{2}{*}{\url{https://misaka-10032.github.io}} & \email{longqicai@gmail.com} \\
& 100 N Whisman Rd, Apt 2121, Mountain View, CA \\
\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\resitem{Google Research}{Mountain View, CA}{Software Engineer}{Mar. 2018 - present}
  \begin{itemize}
    
    \item Image segmentation infrastructure and models.
    \begin{itemize}
      \item Set up the data pipelines to get millions of masks from the crowd workers.
      \item Refactored the image segmentation API for smoother model training and exporting.
      \item Customized the segmentation models for various products: Shopping, Photos, Web Design.
    \end{itemize}
    
    \item Accurate sky segmentation in Google Camera.
    \begin{itemize}
      \item Collected 120k high-accuracy sky masks with active learning and density estimation.
      \item Published a \href{https://google.github.io/sky-optimization/}{paper} and a patent on the technique.
      \item Designed an initialization mechanism to hide the 1s latency during the mode switch.
    \end{itemize}
    
    \item Labeled product retrieval system in Google Lens.
    \begin{itemize}
      \item Fused the visual embeddings and the OCR tokens in the multi-round ranking.
      \item Improved the user satisfaction by 2.3 (out of 5) compared with the SIFT-based system.
    \end{itemize}
  \end{itemize}

\resitem{Google Photos}{Mountain View, CA}{Software Engineer}{Mar. 2017 - Mar. 2018}
  \begin{itemize}
  \item Built the data pipelines for the on-device face clustering.
  \item Implemented the batched processing and the recovery mechanism.
  \item Implemented the global consistency mechanism.
  \end{itemize}

\resitem{Glow, Inc}{Shanghai, China}{Software Engineer Intern}{Jul. 2014 - Jul. 2015}
  \begin{itemize}
  \item Customized the UI widgets and the animations for better user experience.
  \item Implemented the OAuth2 flow for the Google Now Integration.
  \item Set up the internal Maven center, and extracted the common libraries for the team efficiency.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\resitem{Carnegie Mellon University}{Pittsburgh, PA}{M.Sc. in Information Technology Strategy (3.87/4.00)}{Sep. 2015 - Dec. 2016}
\resitem{Fudan University}{Shanghai, China}{B.Sc. in Computer Science and Technology (3.64/4.00)}{Sep. 2011 - Jul. 2015}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\resitem{Partical Systems}{Carnegie Mellon University}{Class project for Compute Graphics}{Dec. 2016}
  \begin{itemize}
  \item Designed the abstraction of a particle system in Javascript.
  \item Implemented two simulation \href{https://misaka-10032.github.io/particle-system/}{examples} based on this abstraction: fireworks and cloth.
  \end{itemize}
\resitem{Halstm}{Carnegie Mellon University}{Class project for Parallel Computer and Architecture Programming}{Apr. - May. 2016}
  \begin{itemize}
  \item Implemented LSTM with Halide.
  \item Exploited the multi-thread execution and SIMD, and achieved 2x speedup.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Languages: C++, Python, Java.
\item Tools: Bash, Git, Mercurial, Bazel, Makefile, Markdown, Latex.
\end{itemize}

\end{document}
